---
title: "Part1_Statical_Inference"
author: "carlos rios"
date: "Wednesday, September 17, 2014"
output: pdf_document
---

## Synopsis
In this work I simulate the exponential distribution and then I investigate the distribution of average of 40 exponentials with parameter lambda = 0.2 

## Libraries
To carry out this work I used the following libraries.

```{r warning=FALSE,message=FALSE}
library("ggplot2")
```

## Simulation
To simulation the exponencial distribution, I take lambda = 0.2 with mean = 1/lambda and standar-deviation = 1/lambda, then I do thousand or so simulated averages of 40 exponentials.

```{r}
lambda<-0.2
popultaionMean<-1/lambda
populationSd<-1/lambda
popupationVar<-1/((lambda)^2)
nosim<-1000
n<-40
sampleMean<-data.frame(x=apply(matrix(rexp(nosim * n,lambda), nosim), 1, mean))

```

### Show where the distribution is centered at and compare it to the theoretical center of the distribution.


```{r}
mean(sampleMean$x)
popultaionMean
```


### Show how variable it is and compare it to the theoretical variance of the distribution.
```{r}
var(sampleMean$x)
popupationVar/n
```


### Show that the distribution is approximately normal.

In order to show how the distribution is approximately normal, I do a histogram with the distribution of averages and then I fit it with a normal distribution.

```{r}
g<-ggplot(sampleMean, aes(x = x))
g<- g + geom_histogram(aes(y = ..density..),binwidth=0.1, position = "stack")  
g<- g + stat_function(fun = dnorm,size=2,colour = "gray",
                      arg = list(mean = popultaionMean,
                                 sd=(sqrt(popupationVar)/sqrt(n)) ))
g<- g +  labs(title="Distribution ",x="")
g

```


### Evaluate the coverage of the confidence interval for 1/lambda: .

```{r}
(mean(sampleMean$x) + c(-1, 1) * qnorm(0.975) * sd(sampleMean$x)/sqrt(n))

```



## Appendix

This work was made with the following environment.
```{r}
sessionInfo()
```
